\begin{abstract}
We are living in a blockchain era where both academic and industry people are interested in blockchain technology. It all started with the introduction of bitcoin by Satoshi Nakamoto; the world's first decentralized cryptocurrency, it can be termed as the first phase of blockchain technology. In the second phase, Ethereum got the success more people got interested in blockchain technology. Now we are in the third phase of the blockchain revolution that is the blockchain for enterprise. Now, every business is trying to take advantage of blockchain technology for their use case, and in this phase, Hyperledger Fabric is the most promising modular enterprise blockchain. It is proven to be very useful, but we noticed that official hyperledger fabric implementation still doesn't support any BFT protocol for consensus (or ordering service) and above all, there is no practical implementation of a Byzantine fault tolerant consensus protocol that can perform in network settings, such as the Internet where the user of the blockchain can not provide network guarantees.\\ In this thesis, We present an alternative, HoneyBadgerBFT as a consensus option in Hyperledger Fabric's Ordering service, the first practical asynchronous BFT protocol, which guarantees liveness without making any timing assumptions about the network. HoneyBadgerBFT can handle up to one-third malicious nodes in the network. We present an implementation and experimental results to show that our protocol can achieve throughput comparable to Raft (a CFT protocol) in standard scenarios and makes progress even when the underlying network is not stable.
\end{abstract}